### 2015-11-17 section/1_under.tex
check in correlation table
finish section 2

The first task we are facing is to figure out a root-cause taxonomy for
real-world inefficient loops. 
Our taxonomy design is guided by checking a benchmark suite of real-world
inefficient loops, collected by previous work \cite{SongOOPSLA2014,PerfBug}. 
We also try to satisfy three requirements in our design.
(1) Coverage: covering
a big portion of real-world inefficient loop problems; 
(2) Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
(3) Generality: too application-specific root causes will not work, as we
need to build diagnosis tools to automatically identify these root causes 
without developers' help.

Note that we are not the first one who tries to categorize
the root causes of performance problems. We are also not the first
to identify many of the root-cause categories below. Instead, guided by
previous work and our empirical study, we try to figure out our own taxonomy 
that satisfy the above three requirements and can
work well with the diagnosis tool that we will build later.

\subsection{Taxonomy}
\label{sec:study_tax}
Our taxonomy contains two major root cause categories,
\textit{resultless} and \textit{redundancy}, and several sub-categories, 
as below.

\underline{\textit{\textbf{Resultless}}}
Resultless loops spend a lot of time in computation that does not 
produce any results that will be used after the loop.
Depending on when such resultless computation is conducted, we further
consider four sub-categories.

{\textbf{0*}}: 
This type of loops never produce any results in any iteration.
This type of loops should be rare in mature software systems.
They should simply be deleted from the program.
%Question: dynamic or static?

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
\caption{A resultless 0*1? bug in Mozilla}
\label{fig:Mozilla347306}
\end{figure}

{\textbf{0*1?}}:
This type of loops only produce results in the last iteration, if any. 
They are often related to search: they check a sequence of elements one
by one until the right one is found.
Not all loops of this type are inefficient. If they are, they are often
fixed by data-structure changes.
Figure~\ref{fig:Mozilla347306} shows an example from Mozilla
JavaScript engine. 
The loop searches through an array containing source code information for the input \texttt{pc}. 
In practice, this loop needs to execute more than 10000 iterations for 
many long JavaScript encountered by users, which leads to huge 
performance problems --- web browsers freeze. To fix this problem, 
developers simply replace array with hash table when processing long
JavaScript files.
% This improve the performance by 52.60{\bf X}.

@@

{\textbf{[0$|$1]*}}:
Every iteration in this type of loops may or may not produce results.
Under certain workload, the majority of the loop iterations do not produce
any results and lead to performance problems perceived by end users.
The inefficiency problem caused by this type of loops can often be solved
by adding extra conditions to skip the loop under certain contexts.
Figure~\ref{fig:GCC46401} shows such an example from GCC.
%how users perceive this problem
%explain how every iteration may or may not produce any results
%explain the fix
Only when the if branch executed,
one iteration will generate results. 
The bug happens when GCC checks violation of sequence point rule. 
The user notice severe performance degradation when enabling the checking. 
The buggy loop is super-linear inefficient in terms of the number of operands
in one expression. The buggy input contains an expression, which is long and special. 
The loop takes a lot of iterations during bad run, but none of the iterations will 
generate results. 
The patch is to add extra checking before processing each operand. When it also has
the special feature like the bad input, the loop will be skipped.

@@

{\textbf{[1]*}}:
Loops in this category always generate results in almost all iterations. 
They are inefficient, because the results generated could be useless due to
some high-level semantic reasons.
Understanding and fixing this type of inefficiency problems often require
deep understanding of the program and are difficult to automate.
For example, several Mozilla performance problems are caused by 
loops that contain intensive GUI operations.
Although every iteration of these loops produce side effects, 
the performance problem forced developers to change the program 
and batch/skip some GUI operations.

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
\caption{A cross-loop redundant bug in Mozilla }
\label{fig:Mozilla477564}
\end{figure}

\underline{\textit{\textbf{Redundant}}}
Redundant loops spend a lot of time in repeating computation that is already
conducted.
Depending on the unit of the redundant computation, we further consider 
two sub-categories.

@@

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla490742.js}}
\caption{A cross-iteration redundant bug in Mozilla }
\label{fig:Mozilla490742}
\end{figure}

{\textbf{Cross-iteration Redundancy}}:
Loop iteration is the redundancy unit here:
one iteration repeats
repeating what was already done by an earlier iteration of the same loop.
Here, we consider recursive function calls as a loop, treating one function 
call instance as one loop iteration. 
This type of inefficiency is often fixed by memoization or batching, depending
on whether the redundancy involves I/O operations.
For example, GCC\#27733 shown in Figure~\ref{fig:GCC27733} 
is fixed by better memoization. 
%Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
%This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
redundancy. The inefficient loop in this case saves one URL into the ``Favorite
Links'' database in each iteration. One database transaction in each iteration
turns out to be to time consuming, with too much redundant work across
iterations. At the end, developers decide to batch all database updates into 
one big transaction, which speeds up some workload like 
bookmarking 50 tabs 
from popping up timeout windows to not blocking.
%xxx from several minutes
%to a couple of seconds.

{\textbf{Cross-loop Redundancy}}:
A whole loop is the redundancy unit here:
one dynamic instance of a loop spends a big chunk, if not all, of its
computation in repeating the work already done by an
earlier instance of the same loop.
Developers often fix this type of inefficiency problems through memoization:
caching the earlier computation results and skip following redundant loops.
Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
The buggy loop is to count how many previous siblings of the input \texttt{aNode} have the same name and URI. 
There is an outer loop for the buggy one, and the outer loop will update \texttt{aNode} by using its next siblings. 
The bug is fixed by saving the calculated count for each node. 
A new count value is calculated by adding one to the saved count value of the nearest previous sibling with the same name and URI.

\subsection{Empirical study}
\label{sec:tax_study}
Having presented our taxonomy above, we will see how it works for a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}. Specifically, we want to check the 
coverage and the actionability of our taxonomy presented above:
(1) How common are real-world performance problems caused by the 
patterns discussed above?
(2) How are real-world problems fixed by developers? Can we predict their
fix strategies based on the root-cause pattern?

\subsubsection{Methodology}
\begin{table}[h!]
\centering
\begin{tabular}{@{\hspace{3pt}}l@{\hspace{3pt}}|@{\hspace{3pt}}c@{\hspace{3pt}}}
\hline
Application Suite Description (language) & \# Bugs \\
\hline                            
{\bf Apache Suite} 	 & 11\\
%\cline{1-1}
{HTTPD:	Web Server (C)	}& \\
{TomCat:  Web Application Server (Java)}& \\
{Ant:	Build management utility (Java)}& \\
%\hline
%JMeter	& Load test utility (Java) & \\
\hline                            
{\bf Chromium Suite} Google Chrome browser (C/C++) & 4\\
\hline
%\multicolumn{2}{|l|}
{\bf GCC Suite}  GCC \& G++ Compiler (C/C++)     & 8\\
\hline
{\bf Mozilla Suite}  & 12\\
%\cline{1-1}
{Firefox: Web Browser (C++, JavaScript)}& 	\\
{Thunderbird: Email Client (C++, JavaScript)}& \\
\hline
{\bf MySQL Suite}     & 10	\\
%\cline{1-1}
{Server: Database Server (C/C++)}&  	\\
%\cline{1}
{Connector: DB Client Libraries (C/C++/Java/.Net)} &  	\\
\hline
{\bf Total}	   & 45 \\
\hline
\end{tabular}
\caption{Applications and bugs used in the study}
\label{tab:app_bug}
\end{table}

Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects, as 
shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here\footnote{The definition of ``loop-related'' in this paper is a little
bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
43 problems as loop-related. }.
More details can be found in the original papers that collect
these bugs.

\subsubsection{Observations}
\label{sec:study_ob}
\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lccccccl|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total&Fix Strategy\\
\hline
Total \# of loop-related bugs & 11 & 4 & 8 & 12 & 10 & 45 &  \\
\hline
\multicolumn{8}{|c|}{\# of {\textit {Resultless}} bugs}\\
\multicolumn{1}{|l}{ {\bf 0*} }
&0&0&0&0&0&0&\\
\multicolumn{1}{|l}{ {\bf 0*1?} }
&0&0&0&2&3&5&C(4)$|$S(1)\\
\multicolumn{1}{|l}{{\bf [0$|$1]*}}
&0&1&1&1&1&4&S(4)\\
\multicolumn{1}{|l}{{\bf 1*}}
&1&2&3&6&3&15& B(4)$|$S(4)$|$O(7)\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
\hline
\multicolumn{8}{|c|}{ \# of {\textit {Redundant}} bugs}\\
\multicolumn{1}{|l}{Cross-{\bf iteration} redundancy}
&7&1&2&1&1&12&B(4)$|$M(7)$|$O(1)\\
\multicolumn{1}{|l}{ Cross-{\bf loop} redundancy}
&3&0&2&2&2&9&B(4)$|$M(5)\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
B, M, S, C, and O represent different fix strategies:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). The numbers in the 
parentheses denote the number of problems that are fixed using specific
fix strategies.}
\label{tab:root}
\end{table*}

\underline{Are the root-causes in our taxonomy common?}
The answer is \textit{yes}.
Resultless loops are about as common as redundant loops
(24 vs. 21).
Intuitively, 0* loops, where no iteration produces any results,
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\underline{How are real-world performance bugs fixed?}
Overall, the fix strategies are well aligned with root-cause patterns.
For example, 
all inefficient loops with resultless [0$|$1]* are
fixed by skipping the loop under certain contexts,
and almost all inefficient loops with redundant root causes are fixed either by 
memoization or batching the computation. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a problem.
The only problem is that there are no silver bullets for 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

\paragraph{Implications}
As we can see, resultless loops and redundant loops are both common reasons
that cause user-perceived performance problems in practice. The root-cause
categories discussed above also match with developers' fix strategy well ---
with a little bit amount of extra analysis, one can pretty much predict the fix strategy based on the root-cause pattern.
Consequently, tools that cover these root causes will have high
chances to satisfy the coverage and accuracy requirements of performance 
diagnosis.

%TODO even for the other, there are things we could do ...

@@

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line developer/user discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
whether the root-cause of a performance problem is related to loops or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

We believe that the bugs in our study provide a representative sample of the 
well-documented and
fixed performance bugs that are user-perceived and loop-related in the studied 
applications. 
Since we did not set up the root-cause taxonomy to fit particular
bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
framework presented below will go beyond these sampled performance bugs.

>>>>

Previous work has identified a wide variety of performance root-cause 
categories. However, no existing taxonomy satisfies all the three 
requirements below and hence cannot be directly used for our diagnosis tool
design.
\begin{enumerate}
\item Coverage: covering
a big portion of real-world inefficient loop problems; 
\item Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
\item Generality: application-specific root causes will not work, as we
hope to build diagnosis tools that can automatically identify root causes 
without developers' help.
\end{enumerate}

This section first presents the root-cause taxonomy designed by us, 
and then discusses the coverage, actionability, and generality
of our taxonomy using a suite of real-world
inefficient loops collected by previous work \cite{SongOOPSLA2014,PerfBug}.

\subsection{Taxonomy Design}
\label{sec:study_tax}
We divide all inefficient loops into two root-cause categories:
\textit{resultless} and \textit{redundancy}.

\subsubsection{Resultless loops}
A resultless loop spends a lot of time in computation without
producing any results useful after the loop.
It is further categorized based on which loop iterations are
(not) producing useful results.

{\textbf{0*}}: 
This type of loops never produce any results in any iteration.
They are rare in mature software systems.
They should simply be deleted from the program.
%Question: dynamic or static?

%\begin{figure}[h]
%\centering
%\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
%     morekeywords={+},keepspaces=true}
%  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
%\caption{A resultless 0*1? bug in Mozilla}
%\label{fig:Mozilla347306}
%\end{figure}

{\textbf{0*1?}}:
This type of loops only produce results in the last iteration, if any. 
They are often related to search: check a sequence of elements one
by one until the right one is found.
Clearly, whether this type of loops are efficient or not depends on the
workload. If they are indeed inefficient, they are often
fixed by data-structure changes.
As an example, Mozilla JavaScript engine used to store the source-code 
line numbers of all byte-code instructions in a linked list \texttt{script}. 
Later on, many users complained that Mozilla browser freezed when opening
some popular websites. It turned out that those websites contained large
JavaScript files that filled the linked list \texttt{script} with
tens of thousands of nodes. Linear search on \texttt{script} then caused the
to freeze. To fix this problem, 
developers simply replace linked list with hash table
(Mozilla Bug\#347306).
% This improve the performance by 52.60{\bf X}.

@@

{\textbf{[0$|$1]*}}:
Each iteration in this type of loops may or may not produce results.
For some workload, the majority of iterations do not produce
results and lead to performance problems perceived by users.
These problems are often solved
by using a simple check to conditionally skip the expensive loop.
Figure~\ref{fig:GCC46401} shows such an example.
%how users perceive this problem
%explain how every iteration may or may not produce any results
%explain the fix
Users complained that compilation became extremely slow when they 
enabled the \texttt{-Wsequence-point} checking.
The slowness was caused
by the \texttt{for} loop shown in the figure. Since the algorithm
behind this loop is quadratic in the number of operands in an expression, 
programs with long expressions suffer severe slow-downs.
After further diagnosis, developers observed that this loop rarely
had any side-effects, as the \texttt{if} condition was rarely satisfied.
At the end, the patch greatly improved performance through a
simple checking that allows the loop to be
skipped for most expressions.

@@

{\textbf{[1]*}}:
Loops in this category always generate results in almost all iterations. 
They are inefficient because their results are useless due to
some high-level semantic reasons.
Understanding and fixing this type of inefficiency problems often require
deep understanding of the program and are difficult to automate.
For example, several Mozilla performance problems are caused by 
loops that contain intensive GUI operations whose graphical outcome may not
be observed by humans and hence can be optimized.

\subsubsection{Redundant loops}
Redundant loops spend a lot of time in repeating computation that is already
conducted. They are further categorized below based on their redundancy unit.

@@

\comment{
\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla490742.js}}
\caption{A cross-iteration redundant bug in Mozilla }
\label{fig:Mozilla490742}
\end{figure}
}

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
\caption{A cross-loop redundant bug in Mozilla }
\label{fig:Mozilla477564}
\end{figure}

{\textbf{Cross-iteration Redundancy}}:
Loop iteration is the redundancy unit here:
one iteration repeats
what was already done by an earlier iteration of the same loop.
Here, we consider a recursive function as a loop, treating one function-call
instance as one loop iteration.

This type of inefficiency is often fixed by memoization or batching, depending
on whether the redundancy involves I/O operations.
For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
redundant computation across different invocations of recursive function
\texttt{mult\_alg}. The patch essentially allows memoization to work.
%Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
%This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
\comment{
Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
redundancy. The inefficient loop in this case saves one URL into the ``Favorite
Links'' database in each iteration. One database transaction in each iteration
turns out to be to time consuming, with too much redundant work across
iterations. At the end, developers decide to batch all database updates into 
one big transaction, which speeds up some workload like 
bookmarking 50 tabs 
from popping up timeout windows to not blocking.
%xxx from several minutes
%to a couple of seconds.
}

{\textbf{Cross-loop Redundancy}}:
A whole loop is the redundancy unit:
one dynamic instance of a loop spends a big chunk, if not all, of its
computation in repeating the work already done by an
earlier instance of the same loop.
Developers often fix this type of inefficiency problems through memoization:
caching the earlier computation results and skip following redundant loops.
Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
The buggy loop counts how many previous siblings of the input \texttt{aNode} have the same name and URI. 
There is an outer loop, not shown in the figure, that repeatedly updates
\texttt{aNode} to be its next sibling and calls
\texttt{sss\_xph\_generate} with the new \texttt{aNode}. 
This bug is fixed by adding an extra field for each node to save the calculated 
count, so that a new count value can be calculated by simply adding one to the
saved count value of the nearest previous sibling with the same name and URI.

\subsection{Taxonomy Assessment}
\label{sec:tax_study}
We assess the coverage, actionability, and generality of our taxonomy using
a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}.

\subsubsection{Methodology}
\begin{table}[h!]
\small{
\centering
\begin{tabular}{@{\hspace{3pt}}l@{\hspace{3pt}}|@{\hspace{3pt}}c@{\hspace{3pt}}}
\hline
Application Suite Description (language) & \# Bugs \\
\hline                            
{\bf Apache Suite} 	 & 11\\
%\cline{1-1}
{HTTPD:	Web Server (C)	}& \\
{TomCat:  Web Application Server (Java)}& \\
{Ant:	Build management utility (Java)}& \\
%\hline
%JMeter	& Load test utility (Java) & \\
\hline                            
{\bf Chromium Suite} Google Chrome browser (C/C++) & 4\\
\hline
%\multicolumn{2}{|l|}
{\bf GCC Suite}  GCC \& G++ Compiler (C/C++)     & 8\\
\hline
{\bf Mozilla Suite}  & 12\\
%\cline{1-1}
{Firefox: Web Browser (C++, JavaScript)}& 	\\
{Thunderbird: Email Client (C++, JavaScript)}& \\
\hline
{\bf MySQL Suite}     & 10	\\
%\cline{1-1}
{Server: Database Server (C/C++)}&  	\\
%\cline{1}
{Connector: DB Client Libraries (C/C++/Java/.Net)} &  	\\
\hline
{\bf Total}	   & 45 \\
\hline
\end{tabular}
}
\caption{Applications and bugs used in the study}
\label{tab:app_bug}
\end{table}

Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects, as 
shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here\footnote{The definition of ``loop-related'' in this paper is a little
bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
43 problems as loop-related. }.
More details can be found in previous papers that collected
these bugs.

\subsubsection{Assessment}
\label{sec:study_ob}

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lcccccc|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\hline
Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
\hline
\multicolumn{1}{|l}{ {\bf 0*} Resultness}
&0&0&0&0&0&0\\
\multicolumn{1}{|l}{ {\bf 0*1?} Resultness}
&0&0&0&2&3&5\\
\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultness}
&0&1&1&1&1&4\\
\multicolumn{1}{|l}{{\bf 1*} Resultness}
&1&2&3&6&3&15\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
\hline
\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&12\\
\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&9\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
}
\label{tab:root}
\end{table*}

\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
%For ranges 0-10, multiply by 10 by adding 0 after #1

\begin{table}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lcccccc}
%\hline
                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
%\hline
 B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
%\hline
 M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
 S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
 C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
 O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
%\hline

\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs fixed by each strategy:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). 
``C-I'': cross- iteration redundancy. 
``C-L'': cross-loop redundancy. 
}
\label{tab:correlation}
\end{table}

\paragraph{Coverage}
Our taxonomy does cover all inefficient loops under study. 
Resultless loops are about as common as redundant loops
(24 vs. 21).
Intuitively, 0* loops, where no iteration produces any results,
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\paragraph{Actionability}
As demonstrated in Table \ref{tab:correlation}, 
the root-cause categories in our taxonomy are highly correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultness loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

\paragraph{Generality}
The root-cause categories in our taxonomy are designed to be 
generic. Table \ref{tab:root} also shows that these categories 
each appears in multiple
application in our study. The only exception is $0^*$-resultless, which
never appears.

In summary, the study above informally demonstrates that our taxonomy
is suitable to guide our design of \Tool.
%chances to satisfy the coverage and accuracy requirements of performance 
%diagnosis.
%
%TODO even for the other, there are things we could do ...

@@

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
whether the root-cause of a performance problem is related to loops or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

\comment{
We believe that the bugs in our study provide a representative sample of the 
well-documented and
fixed performance bugs that are user-perceived and loop-related in the studied 
applications. 
Since we did not set up the root-cause taxonomy to fit particular
bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
framework presented below will go beyond these sampled performance bugs. 
}
